### 2020-06-01 case-studies.tex
beginning of live evaluation section

\subsection{Case Study: Grading with Livelits}\label{sec:live-grading}
\begin{figure}
\begin{lstlisting}
let grades = $dataframe in 
            A1          A2          A3          A4       Midterm      Final  +
  Cyrus
  Nick
  David
    + 
let averages = compute_averages(grades) in 
let cutoffs = $cutoffs(averages) in

@@

To avoid this situation, the livelit expansion mechanism 
maintains parameter and splice hygiene: parameters and splices are included in the expansion 
in a capture-avoiding manner.
Consequently, clients can reason abstractly about binding in splices: variables in splices
always refer to bindings visible to the client, rather than bindings that are hidden inside expansions.
This is implemented by alpha-renaming bindings internal to the expansion as necessary.
(We discuss potentially relaxed variations of this hygiene discipline in Sec.~\ref{sec:discussion}).
\subsubsection{Live Evaluation}\label{sec:live-evaluation}

>>>>

\subsection{Case Study: Grading with Livelits}\label{sec:live-grading}
\begin{figure}
\begin{lstlisting}
let weights = [0.1, 0.1, 0.1, 0.1, 0.25, 0.35] in 
let grades = $dataframe in 
            A1          A2          A3          A4       Midterm      Final  +
  Cyrus
  Nick
  David
    + 
let averages = compute_averages(grades, weights) in 
let cutoffs = $cutoffs(averages) in

@@

To avoid this situation, the livelit expansion mechanism 
maintains parameter and splice hygiene: parameters and splices are included in the expansion 
in a capture-avoiding manner.
Consequently, clients can reason abstractly about binding in splices: variables in splices
always refer to bindings visible to the client, rather than bindings that are hidden inside expansions.
This is implemented by alpha-renaming bindings internal to the expansion as necessary.
(We discuss potentially relaxed variations of this hygiene discipline in Sec.~\ref{sec:discussion}.)

\subsubsection{Live Evaluation}\label{sec:live-evaluation}
Livelits can request the result of evaluating a splice or parameter.
However, evaluation is, as usual, defined only for closed expressions, 
whereas parameters and splices can both refer to variables in the surrounding
context. In order to provide evaluation results for these free variables, 
Hazel performs \textbf{closure collection}. This proceeds in two phases.

In the first phase, Hazel evaluates the program with holes appearing in place of each livelit 
application and collects closures around each of these holes \cite{HazelnutLive}. 
For example, the closure around the application of \li{\$dataframe} in Fig.~\ref{fig:grading}
contains the value of the \li{weights} variable from Line 1 and any other bound variables, e.g. 
from imported libraries, not shown. Consequently, when the livelit requests the evaluation result for
splices that use these variables, such as the cell shown selected in Fig.~\ref{fig:grading}, their values are available.

The closure for the \li{\$cutoffs} livelit in Fig.~\ref{fig:grading} includes a binding for 
the \li{grades} variable. However, this variable's evaluation result, along with the evaluation 
results for other variables that depend on \li{grades}, such as \li{averages}, ultimately depend on the 
expansion of the \li{\$dataframe} livelit. If we stop after the first phase of closure collection,
then no useful result will be available here because that livelit has been replaced with a hole.
For this reason, there is a second phase of closure collection where any livelit holes that appear 
in the collected closures are \emph{resumed}, i.e. the expansion is generated 
(in this case, for the \li{\$dataframe} livelit) and is used to fill 
the hole before evaluation resumes, following the semantics for resumption developed by \citet{HazelnutLive}.
Livelit expansions do not themselves contain livelits, so no subsequent resumption phases are necessary.
